Reduced diversity and increased specialzation of Alaska salmon fishermen:

### 2016-10-06 salmon/paper/salmon_paper.Rmd
paper

ggplot(data=rbind(df.gen,df.spec), aes(year, mean, group=strategy, fill=strategy)) + geom_ribbon(aes(ymin=low,ymax=hi), alpha=0.5)

@@

yearpermit$b0 = apply(est$b0_str_yr,2,median)
yearpermit$b0_low = apply(est$b0_str_yr,2,quantile,0.25)
yearpermit$b0_hi = apply(est$b0_str_yr,2,quantile,0.75)

ggplot(data=yearpermit) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + ylab("Intercepts on mean")
```

@@

@@

for(i in 1:nrow(df)) {
  tmp = est$b0_str_yr[,b0_indx[i]] + 
    x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]]+est$b1_str_yr_mu) +
    x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)# +
    #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.25)
  df$high[i] = quantile(tmp,0.75)
}

ggplot(df[df$permits=="S01E",], aes(x=x,y=pred,group=years)) +
  #geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  geom_line() +
  facet_wrap(~years) + xlab("Previous species diversity") + ylab("Predicted benefit of adding +1 spp (ln $)")

@@

for(i in 1:nrow(df)) {
  tmp = est$b0_str_yr[,b0_indx[i]] + 
    x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]]+est$b1_str_yr_mu) +
    x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)# +
    #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.25)
  df$high[i] = quantile(tmp,0.75)
}

ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted benefit of adding +1 spp (ln $)")

@@

for(i in 1:nrow(df)) {
  tmp = est$g0 + est$g0_strategy[,df$permit[i]] + x1[df$diversity[i]] * (est$g_1[,df$year[i], df$permit[i]]+est$g1_str_yr_mu) +
    x2[df$diversity[i]] * (est$g_2[,df$year[i], df$permit[i]]+est$g2_str_yr_mu)# +
  #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.25)
  df$high[i] = quantile(tmp,0.75)
}

ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted benefit of adding +1 spp (ln $)")

>>>>

ggplot(data=rbind(df.gen,df.spec), aes(year, mean, group=strategy, fill=strategy)) + geom_ribbon(aes(ymin=low,ymax=hi), alpha=0.5) + geom_hline(yintercept=0, color="red")

@@

yearpermit$b0 = apply(est$b0_str_yr,2,median)
yearpermit$b0_low = apply(est$b0_str_yr,2,quantile,0.025)
yearpermit$b0_hi = apply(est$b0_str_yr,2,quantile,0.975)

ggplot(data=yearpermit) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + 
  ylab("Intercepts on mean") + 
  geom_hline(yintercept=0, color="red")
```

@@

specdiv.prev = seq(1, 5, by=0.1)
specdiv = specdiv.prev + 1 # always add 1 more in these comparisons
x1 = log(specdiv/specdiv.prev)
x2 = log(specdiv/specdiv.prev) * specdiv.prev

@@

for(i in 1:nrow(df)) {
  tmp = x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]]+est$b1_str_yr_mu) + x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)

  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.025)
  df$high[i] = quantile(tmp,0.975)
}

ggplot(df[df$permits=="S01E",], aes(x=x,y=pred,group=years)) +
  #geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  geom_line() +
  facet_wrap(~years) + xlab("Previous species diversity") + ylab("Predicted benefit of adding +1 spp (ln $)") + geom_hline(yintercept=0, color="red")

@@

for(i in 1:nrow(df)) {
  tmp = est$b0_str_yr[,b0_indx[i]] + 
    x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]]+est$b1_str_yr_mu) +
    x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)# +
    #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.025)
  df$high[i] = quantile(tmp,0.975)
}

ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted benefit of adding +1 spp (ln $)") + geom_hline(yintercept=0, color="red")

@@

for(i in 1:nrow(df)) {
  tmp = est$g0 + est$g0_strategy[,df$permit[i]] + x1[df$diversity[i]] * (est$g_1[,df$year[i], df$permit[i]]+est$g1_str_yr_mu) +
    x2[df$diversity[i]] * (est$g_2[,df$year[i], df$permit[i]]+est$g2_str_yr_mu)# +
  #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.025)
  df$high[i] = quantile(tmp,0.975)
}

ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted marginal benefit of adding +1 spp (ln $)")
